---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse  = TRUE,
  comment   = "#>",
  fig.path  = "man/figures/",
  out.width = "100%"
)
```



# cleaner


<!-- badges: start -->
[![License: GPL (>= 2)](https://img.shields.io/badge/License-GPL%20%28%3E%3D%202%29-blue.svg)](https://choosealicense.com/licenses/gpl-2.0/)
[![Dependencies](https://img.shields.io/badge/dependencies-5/119-orange?style=flat)](#)
<!-- badges: end -->


Research compendium to automatically detects duplicated bibliographic references 
using the package [revtools](https://revtools.net/).



### Content

This repository is structured as follow:

- [`data/`](https://github.com/FRBCesab/cleaner/tree/master/data):
contains all raw data required to perform analyses

- [`analyses/`](https://github.com/FRBCesab/cleaner/tree/master/analyses/):
contains R scripts to run each step of the workflow

- [`outputs/`](https://github.com/FRBCesab/cleaner/tree/master/outputs):
contains all the results created during the workflow

- [`DESCRIPTION`](https://github.com/FRBCesab/cleaner/tree/master/DESCRIPTION):
contains project metadata (author, date, dependencies, etc.)

- [`make.R`](https://github.com/FRBCesab/cleaner/tree/master/make.R):
master R script to run the entire project by calling each R script stored in 
the `analyses/` folder



### Usage

Clone the repository, open the `.Rproj` file in RStudio and run:

```{r eval = FALSE}
source("make.R")
```



### Notes

- All required packages, listed in the `DESCRIPTION` file, will be installed (if necessary)
- All required packages and R functions will be loaded
- Some analyses listed in the `make.R` might take time
